\chapter{Non-relational monotonic finitary static analysis 1}

\begin{itemize}
	\item{\textbf{Design of a non-relational abstract interpreter for SIL} : Non-relational abstraction deals with having a point-wise independent abstraction function for the latttice elements or  the set of the states.

	this may be understod as catersian abstraction or component wise abstraction trying ot represnt the different point in the cartesian plane.

	the resulting states are not related.
	}

	\item{\textbf{Forward non-relational finitary reachability static analysis of SIL} :
	non-relational is easy to program but is less approximate.
	relational is cost effective but difficult to program. Global non-relational and local relational finitary analysis is caaried out.

	non-relational finitary analysis of set of environments result in having a less precise set of states. the galois connection is used to improve the approximation of co-domain. To form the approximate lattice a composition of various galois connection is used. this abstract lattice is then used eliminate abstract 'useless' enviromments. 

	}

	\item{\textbf{Forward non-relational finitary reachability static analysis of arithmetic expressions} : picking up from previous chapter on static analysis of arithmetic expressions, this part deals with forming structural definitions of evaluation of arithmetic expression semantics.
	}

	\item{\textbf{Forward non-relational finitary reachability static analysis of boolean expressions} : extends the structural definitions for the static analysis of boolean expressions semantics.
	}

	\item{\textbf{Forward non-relational finitary reachability static analysis ofcommands} : extends the structural definitions for the static analysis of commands, the precondition and the post condition analysis of the commands.
	}

	\item{\textbf{initialization and simple sign analysis} : is simply defining rules for the mathematical sign allotment for the number. 
	}

	\item{\textbf{Ocaml implementation of abstract interpreter}.  
	}

\end{itemize}