\chapter{Ordered Maps Galois Connections 2}

\begin{itemize}

	\item{\textbf{Poset Images} : 
	image of complete lattice by join preserving maps is a complete lattice.

	image of complete lattice by closure operators is also a complete lattice.
	}

	\item{\textbf{Closure Operator induced by Moore Family} : closure operator on a lattice induces a moore family if glb is preserved in the lattice as well as the moore family.
	}

	\item{\textbf{closure operator on monotonic functions} : least upper closure operator is said to exist for monotonous maps, if f(y) is less than or greater than y \& y  is less than or greater than x. for a map pair (x,y).
	}

	\item{\textbf{Complete lattice of Galois Connections} : complete set of upper closure operators on complete lattice is also a complete lattice.

	in terms of galois connections the effort was put to explain the importance of galois connection preservance while the transformation through closure operators take place.
	}


	\item{\textbf{bifinitary traces} :
	set of finite , finite non-empty sequences.
	}

	\item{\textbf{prefix closure} : prefixes, pre conditions of bifinitary traces.
	}

	\item{\textbf{limits of chain of traces} : unique limit exists for an increasing finite chain of traces.
	}

	\item{\textbf{There exists a galois connection between sets of bifinitary traces and their prefix closures.}
	}

	\item{\textbf{limits of bifinitary traces} :  lim acts as a topological closire operator on the posets.
	}

	\item{\textbf{closure of prefix and limits} : composition of prefix closure operator and the lim is a topological closure operator.
	}

	\item{\textbf{complete lattice of Safety Properties} : safety property is a complete lattice but not necessarily a complete join morphism. 

	It is possible to disprove a safety property by looking at a finite part of program behavior . 
	}

\end{itemize}

